---
title             : "The title"
shorttitle        : "Title"

author: 
  - name          : "Laura Fernandez Arroyo"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "my@email.com"
  - name          : "Nuria Sagarra"
    affiliation   : "1"
  - name          : "Cristina Lozano-Argüelles"
    affilitation  : "2"

affiliation:
  - id            : "1"
    institution   : "Rutgers University"
  - id            : "2"
    institution   : "John Jay College/CUNY"



keywords          : ""
wordcount         : ""



floatsintext      : yes
figurelist        : yes
tablelist         : yes
footnotelist      : yes
linenumbers       : yes
mask              : yes
draft             : yes

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_word
---

```{r setup, include = FALSE}
library("papaja")
library("officer")
library("flextable")
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

```{r, 'source-scripts-models'}
source(here::here("scripts", "02_load_data.R"))
source(here::here("scripts", "01_helpers.R"))

# Get path to saved models
gca_mods_path  <- here("mods", "stress", "gca")

# Load models as list and store full mod to global env
load(paste0(gca_mods_path, "/model_preds.Rdata"))
load(paste0(gca_mods_path, "/gca_full_mods.Rdata"))
load(paste0(gca_mods_path, "/nested_model_comparisons.Rdata"))

```






# Journal of Memory and Language article (stress, natives and late advanced and intermediate EN y Ma Ch

## Overview

This document contains updates to the statistical analysis for stress_unrelated experiment 
(draft for ISB). 
Last updated on `r Sys.Date()`. 
The results section can be copied and pasted into the corresponding google doc. 
The tables can also be copy and pasted where appropriate. 

## Main changes

**Participants**  



**Analyses**  










# Plots

```{r, 'plot-ind-preds', echo=FALSE, fig.cap="Growth curve analysis estimates of fixations on target as a function of lexical stress for each group during the analysis window. Lines represent model estimates, and the transparent ribbons represent ±SE. Empirical logit values on y-axis correspond to proportions of 0.12, 0.50, 0.88, and 0.98. The horizontal dotted line represents the 50% probability of fixating on the targets. The vertical dotted line indicates 200 ms after the offset of the target syllable."}
knitr::include_graphics(
  here("figs", "stress", "gca", "stress_p2.png")
)
```

```{r, 'plot-group-preds', echo=FALSE, fig.cap="Growth curve analysis estimates of fixations on the target as a function of lexical stress for each group during the analysis window. Symbols and lines represent model estimates, and the ribbons represent ±SE. Empirical logit values on y-axis correspond to proportions of 0.12, 0.50, 0.88, and 0.98. The horizontal dotted line represents the 50% probability of fixating on the targets. The vertical dotted line indicates 200 ms after the offset of the target syllable."}
knitr::include_graphics(
  here("figs", "stress", "gca", "stress_p3.png")
)
```













# Tables 

## Model estimates at target syllable offset  


```{r, table-target-offset-props, eval=T, echo=F}

border_1 <- fp_border(width = 1.5)
border_2 <- fp_border(width = 0.75)

model_preds$target_offset_preds %>% 
  mutate(cond = if_else(stress == 1, "present", "preterit"),
         group = fct_relevel(group, "SS", "AE", "AM", "IE", "IM")) %>% 
  arrange(group, desc(stress)) %>% 
  mutate(group = blank_same_as_last(as.character(group))) %>% 
  select(Group = group, `Lexical stress` = cond, Probability = prob, LB = prob_lb, 
         UB = prob_ub) %>% 
  flextable() %>% 
  width(., j = c(2, 3, 4), width = c(1.1, 1.3, 1.1)) %>% 
  font(., fontname = "Times", part = "all") %>%
  fontsize(., size = 11) %>% 
  border_remove(.) %>%  
  border(., part = "header", 
            border.top = border_1,
            border.bottom = border_2) %>% 
  hline_bottom(., part = "body", border = border_1)
```

*Table 1*: Model estimates for probability of target fixations ±SE at 200 ms 
after the target syllable offset. (LB = lower bound; UP = upper bound)




## Fixed effects

```{r, warning=F}

# Get full mod and make it pretty for the table
pretty_fixed_effects <- gca_full_mods$gca_full_mod_int_2 %>% 
  tidy_lme4() %>% 
  mutate(p = format_pval(p), 
         Parameter = fix_param_names(Parameter)) %>% 
  mutate_each(funs(format_fixef_num), Estimate:t) %>% 
  rename(`_t_` = t, `_p_` = p) 

# Include gammas (Gij) after each parameter name
subs <- c(paste0(0:3, 0), paste0(0:3, 1), 
          paste0(0:3, 2), paste0(0:3, 3), 
          paste0(0:3, 4), paste0(0:3, 5), 
          paste0(0:3, 6))
var_labels <- parenthesize(paste0(emphasize("&gamma;"), "~", subs, "~"))
pretty_fixed_effects$Parameter %<>% paste(., var_labels)

pretty_fixed_effects %>% 
  knitr::kable(format = "pandoc", align = str_tokenize("lrrrr")) 

```

Appendix 1: Growth curve model fixed effects






## Random effects

```{r, 'ranef-table', results = "asis"}
ranef_table <- gca_full_mods$gca_full_mod_int_2 %>% 
  tidy_ranef_summary %>% 
  # Format the numbers
  mutate_each(funs(format_fixef_num), vcov, sdcor) %>%
  mutate_each(funs(format_cor), -var1, -grp, -vcov, -sdcor) %>%
  sort_ranef_grps %>%
  # Format variable names and group names
  mutate(var1 = fix_param_names(var1) %>% blank_nas,
         grp =  blank_same_as_last(grp) %>% fix_param_names) %>% 
  rename(Group = grp, Parameter = var1, Variance = vcov, SD = sdcor)

# Correlation columns need names with characters so that pandoc can align them
names(ranef_table)[5:9] <- 
  c("Correlations", "&nbsp;", " &nbsp;", "  &nbsp;", "  &nbsp;")

ranef_table %>% 
  knitr::kable(format = "pandoc", align = str_tokenize("llrrrrrr"))
```

Appendix 2: Growth curve model random effects




## Pairwise comparisons

```{r, 'learner-comparison-adv'}
########  AES and AMS 

# make table for printing
pairwise_comp_adv <- gca_full_mods$gca_full_mod_int_2_aes %>% 
  tidy_lme4 %>% 
  rename(B = Estimate) %>% 
  filter(str_detect(Parameter, "ams") == TRUE) 

# Add subscript column, convert to rownames, and then add it again
pairwise_comp_adv$subscript <- c(paste0(0:3, 8), paste0(0:1, 9))
pairwise_comp_adv <- tibble::column_to_rownames(pairwise_comp_adv, 'subscript')
pairwise_comp_adv$subscript <- c(paste0(0:3, 8), paste0(0:1, 9))


# Shortcut for inline reporting from the above table
report_pairwise_adv <- function(row_name) report_fixef_row(pairwise_comp_adv, row_name)

```


```{r, pairwise-comp-table-adv, results='asis', eval=T}

# Make table for appendix
pretty_pairwise_table_adv <- gca_full_mods$gca_full_mod_int_2_aes %>% 
  tidy_lme4 %>% 
  mutate(p = format_pval(p), 
         Parameter = fix_param_names(Parameter)) %>% 
  mutate_each(funs(format_fixef_num), Estimate:t) %>% 
  rename(`_t_` = t, `_p_` = p) %>% 
  filter(str_detect(Parameter, "AM") == TRUE) 

pretty_pairwise_table_adv$Parameter %<>% str_replace("Group AE", "AE - AM")

# Include gammas after each parameter name
pw_subs <- c(paste0(0:3, 8), paste0(0:1, 9))
pw_var_labels <- parenthesize(paste0(emphasize("&gamma;"), "~", pw_subs, "~"))
pretty_pairwise_table_adv$Parameter %<>% paste(., pw_var_labels)

pretty_pairwise_table_adv %>% 
  knitr::kable(format = "pandoc", align = str_tokenize("lrrrr")) 

```

Appendix 3a: Pairwise comparisons between advanced learner groups (AE reference). 


```{r, 'learner-comparison_ch'}
########### AMS and IMS

# make table for printing
pairwise_comp_ch <- gca_full_mods$gca_full_mod_int_2_ams %>% 
  tidy_lme4 %>% 
  rename(B = Estimate) %>% 
  filter(str_detect(Parameter, "ims") == TRUE) 

# Add subscript column, convert to rownames, and then add it again
pairwise_comp_ch$subscript <- c(paste0(0:3, 8), paste0(0:1, 9))
pairwise_comp_ch <- tibble::column_to_rownames(pairwise_comp_ch, 'subscript')
pairwise_comp_ch$subscript <- c(paste0(0:3, 8), paste0(0:1, 9))


# Shortcut for inline reporting from the above table
report_pairwise_ch <- function(row_name) report_fixef_row(pairwise_comp_ch, row_name)

```


```{r, pairwise-comp-table-ch, results='asis', eval=T}

# Make table for appendix
pretty_pairwise_table_ma <- gca_full_mods$gca_full_mod_int_2_ams %>% 
  tidy_lme4 %>% 
  mutate(p = format_pval(p), 
         Parameter = fix_param_names(Parameter)) %>% 
  mutate_each(funs(format_fixef_num), Estimate:t) %>% 
  rename(`_t_` = t, `_p_` = p) %>% 
  filter(str_detect(Parameter, "IM") == TRUE) 

pretty_pairwise_table_ma$Parameter %<>% str_replace("Group AM", "AM - IM")

# Include gammas after each parameter name
pw_subs <- c(paste0(0:3, 8), paste0(0:1, 9))
pw_var_labels <- parenthesize(paste0(emphasize("&gamma;"), "~", pw_subs, "~"))
pretty_pairwise_table_ma$Parameter %<>% paste(., pw_var_labels)

pretty_pairwise_table_ma %>% 
  knitr::kable(format = "pandoc", align = str_tokenize("lrrrr")) 

```
Appendix 3b: Pairwise comparisons between Mandarin Chinese learner groups (AM reference).

```{r, 'learner-comparison-en'}
########### AES and IES

# make table for printing
pairwise_comp_en <- gca_full_mods$gca_full_mod_int_2_aes %>% 
  tidy_lme4 %>% 
  rename(B = Estimate) %>% 
  filter(str_detect(Parameter, "ies") == TRUE) 

# Add subscript column, convert to rownames, and then add it again
pairwise_comp_en$subscript <- c(paste0(0:3, 8), paste0(0:1, 9))
pairwise_comp_en <- tibble::column_to_rownames(pairwise_comp_en, 'subscript')
pairwise_comp_en$subscript <- c(paste0(0:3, 8), paste0(0:1, 9))


# Shortcut for inline reporting from the above table
report_pairwise_en <- function(row_name) report_fixef_row(pairwise_comp_en, row_name)

```


```{r, pairwise-comp-table-en, results='asis', eval=T}
# Make table for appendix
pretty_pairwise_table_en <- gca_full_mods$gca_full_mod_int_2_aes %>% 
  tidy_lme4 %>% 
  mutate(p = format_pval(p), 
         Parameter = fix_param_names(Parameter)) %>% 
  mutate_each(funs(format_fixef_num), Estimate:t) %>% 
  rename(`_t_` = t, `_p_` = p) %>% 
  filter(str_detect(Parameter, "IE") == TRUE) 

pretty_pairwise_table_en$Parameter %<>% str_replace("Group AE", "AE - IE")

# Include gammas after each parameter name
pw_subs <- c(paste0(0:3, 8), paste0(0:1, 9))
pw_var_labels <- parenthesize(paste0(emphasize("&gamma;"), "~", pw_subs, "~"))
pretty_pairwise_table_en$Parameter %<>% paste(., pw_var_labels)

pretty_pairwise_table_en %>% 
  knitr::kable(format = "pandoc", align = str_tokenize("lrrrr")) 

```
Appendix 3c: Pairwise comparisons between EN learners (AE reference).


```{r, 'learner-comparison-int'}
########### IES and IMS

# make table for printing
pairwise_comp_int <- gca_full_mods$gca_full_mod_int_2_ies %>% 
  tidy_lme4 %>% 
  rename(B = Estimate) %>% 
  filter(str_detect(Parameter, "ims") == TRUE) 

# Add subscript column, convert to rownames, and then add it again
pairwise_comp_int$subscript <- c(paste0(0:3, 8), paste0(0:1, 9))
pairwise_comp_int <- tibble::column_to_rownames(pairwise_comp_int, 'subscript')
pairwise_comp_int$subscript <- c(paste0(0:3, 8), paste0(0:1, 9))


# Shortcut for inline reporting from the above table
report_pairwise_int <- function(row_name) report_fixef_row(pairwise_comp_int, row_name)

```


```{r, pairwise-comp-table-int, results='asis', eval=T}
# Make table for appendix
pretty_pairwise_table_int <- gca_full_mods$gca_full_mod_int_2_ies %>% 
  tidy_lme4 %>% 
  mutate(p = format_pval(p), 
         Parameter = fix_param_names(Parameter)) %>% 
  mutate_each(funs(format_fixef_num), Estimate:t) %>% 
  rename(`_t_` = t, `_p_` = p) %>% 
  filter(str_detect(Parameter, "IM") == TRUE) 

pretty_pairwise_table_int$Parameter %<>% str_replace("Group IE", "IE - IM")

# Include gammas after each parameter name
pw_subs <- c(paste0(0:3, 8), paste0(0:1, 9))
pw_var_labels <- parenthesize(paste0(emphasize("&gamma;"), "~", pw_subs, "~"))
pretty_pairwise_table_int$Parameter %<>% paste(., pw_var_labels)

pretty_pairwise_table_int %>% 
  knitr::kable(format = "pandoc", align = str_tokenize("lrrrr")) 

```
Appendix 3d: Pairwise comparisons between intermediate learner groups (IE reference).





# 5. Results

```{r, 'write-up-prep', warning=F, eval=T}
# Prepare table to support easy in-line printing of equations
# params <- pretty_fixed_effects %>% 
#  rename(B = Estimate)

params <- gca_full_mods$gca_full_mod_int_2 %>% 
  tidy_lme4() %>% 
  rename(B = Estimate)

params$subscript <- 
  c(paste0(0:4, 0), paste0(0:4, 1), 
    paste0(0:4, 2), paste0(0:3, 3), 
    paste0(0:3, 4), paste0(0:3, 5), 
    paste0(0:3, 6))

params <- tibble::column_to_rownames(params, 'subscript')

params$subscript <- 
  c(paste0(0:4, 0), paste0(0:4, 1), 
    paste0(0:4, 2), paste0(0:3, 3), 
    paste0(0:3, 4), paste0(0:3, 5), 
    paste0(0:3, 6))

# Shortcut for inline reporting from the above table
report_row <- function(row_name) report_fixef_row(params, row_name)

# Pre-calculate intercept as proportion
b0 <- params$B[params$subscript == "00"] %>% as.numeric
b0_prop <- b0 %>% inv_logit %>% round(2) %>% remove_leading_zero

```


SS speakers results are presented first, followed by comparisons between L2 groups. 
The summary for the full model of the Growth Curve Analysis is in the Appendices 2 and 3.
The model also estimated the probability of fixations on the target at the offset of the first syllable in the verb; the probabilities were estimated for each group in both lexical stress conditions (see Table 1; stressed syllable = present, unstressed syllable = preterit).
These probabilities are contained in Table 1.

The model intercept estimates the log odds of SS fixating their gaze on the target averaging across lexical stress condition and time course (*&gamma;*~00~&nbsp;=&nbsp;`r pretty_fixed_effects[1,3]`, SE =&nbsp;`r pretty_fixed_effects[1,4]`. *t* = `r pretty_fixed_effects[1,5]`, *p* = `r pretty_fixed_effects[1,6]`) with a probability of `r printnum(model_preds$target_offset_preds[1,6])` (LB = `r printnum(model_preds$target_offset_preds[1,7])`, UB = 
`r printnum(model_preds$target_offset_preds[1,8])`) in the present tense and of probability = `r printnum(model_preds$target_offset_preds[2,6])` (LB = `r printnum(model_preds$target_offset_preds[2,7])`, UB = 
`r printnum(model_preds$target_offset_preds[2,8])`) in the preterit tense.
The value for the intercept along with the probabilities suggest that SS were anticipating correctly.

There was a main effect of group indicating that L2 speakers predicted less than SS (AE: *&gamma;*~01~&nbsp;=&nbsp;`r pretty_fixed_effects[5,3]`, SE =&nbsp;`r pretty_fixed_effects[5,4]`. *t* = `r pretty_fixed_effects[5,5]`, *p* = `r pretty_fixed_effects[5,6]`; AM: *&gamma;*~11~&nbsp;=&nbsp;`r pretty_fixed_effects[6,3]`, SE =&nbsp;`r pretty_fixed_effects[6,4]`. *t* = `r pretty_fixed_effects[6,5]`, *p* = `r pretty_fixed_effects[6,6]`; IE: *&gamma;*~21~&nbsp;=&nbsp;`r pretty_fixed_effects[7,3]`, SE =&nbsp;`r pretty_fixed_effects[7,4]`. *t* = `r pretty_fixed_effects[7,5]`, *p* = `r pretty_fixed_effects[7,6]`; IM: *&gamma;*~31~&nbsp;=&nbsp;`r pretty_fixed_effects[8,3]`, SE =&nbsp;`r pretty_fixed_effects[8,4]`. *t* = `r pretty_fixed_effects[8,5]`, *p* = `r pretty_fixed_effects[8,6]`).
The two fit plots in Figure 3 reflect this trend in both tenses.
The estimates for the intercept demonstrate that IM was the group that most differed from SS in their ability to anticipate. 
As seen in Figure 3, the fixation log odds for SS crosses the intercept at a higher point than the log odds for the L2 groups, indicating that SS were fixating more on the target verb at the offset of the first syllable. 
The estimated probabilities suggest nonetheless that all L2 groups were still anticipating, except for IM in the present tense (AE x present: probability = `r printnum(model_preds$target_offset_preds[3,6])`, LB = `r printnum(model_preds$target_offset_preds[3,7])`, UB = `r printnum(model_preds$target_offset_preds[3,8])`; AE x preterit: probability = `r printnum(model_preds$target_offset_preds[4,6])`, LB = `r printnum(model_preds$target_offset_preds[4,7])`, UB = `r printnum(model_preds$target_offset_preds[4,8])`; AM x present: probability = `r printnum(model_preds$target_offset_preds[5,6])`, LB = `r printnum(model_preds$target_offset_preds[5,7])`, UB = `r printnum(model_preds$target_offset_preds[5,8])`; AM x preterit: probability = `r printnum(model_preds$target_offset_preds[6,6])`, LB = `r printnum(model_preds$target_offset_preds[6,7])`, UB = `r printnum(model_preds$target_offset_preds[6,8])`; IE x present: probability = `r printnum(model_preds$target_offset_preds[7,6])`, LB = `r printnum(model_preds$target_offset_preds[7,7])`, UB = 
`r printnum(model_preds$target_offset_preds[7,8])`; IE x preterit: probability = `r printnum(model_preds$target_offset_preds[8,6])`, LB = `r printnum(model_preds$target_offset_preds[8,7])`, UB = 
`r printnum(model_preds$target_offset_preds[8,8])`; IM x present: probability = `r printnum(model_preds$target_offset_preds[9,6])`, LB = `r printnum(model_preds$target_offset_preds[9,7])`, UB = 
`r printnum(model_preds$target_offset_preds[9,8])`; IM x preterit: probability = `r printnum(model_preds$target_offset_preds[10,6])`, LB = `r printnum(model_preds$target_offset_preds[10,7])`, UB = 
`r printnum(model_preds$target_offset_preds[10,8])`).

There was also a main effect of the linear term and of the cubic term (*&gamma;*~10~&nbsp;=&nbsp;`r pretty_fixed_effects[2,3]`, SE =&nbsp;`r pretty_fixed_effects[2,4]`. *t* = `r pretty_fixed_effects[2,5]`, *p* = `r pretty_fixed_effects[2,6]`; *&gamma;*~30~&nbsp;=&nbsp;`r pretty_fixed_effects[4,3]`, SE =&nbsp;`r pretty_fixed_effects[4,4]`. *t* = `r pretty_fixed_effects[4,5]`, *p* = `r pretty_fixed_effects[4,6]`, respectively).
These two effects indicate that the slopes were bowed differently across groups—slopes were steeper and bows more closed in the L2 groups (see Fig. 3).
The interactions in the linear and cubic polynomial time terms reflect the sigmoid shape of the time course and were retained in the model because they improved the model fit (*&beta;*&nbsp;=&nbsp;16.939, *df*&nbsp;=&nbsp;4, *p*&nbsp;=&nbsp;.002).
Keeping these interactions yielded an effect caused by the group AE in the linear term (*&gamma;*~12~&nbsp;=&nbsp;`r pretty_fixed_effects[10,3]`, SE =&nbsp;`r pretty_fixed_effects[10,4]`. *t* = `r pretty_fixed_effects[10,5]`, *p* = `r pretty_fixed_effects[10,6]`), revealing that AE increased their gaze fixations on the target faster than any other group once they started anticipating (see Fig. 3).
There was also an effect of all groups in the quadratic term (AE: *&gamma;*~13~&nbsp;=&nbsp;`r pretty_fixed_effects[14,3]`, SE =&nbsp;`r pretty_fixed_effects[14,4]`. *t* = `r pretty_fixed_effects[14,5]`, *p* = `r pretty_fixed_effects[14,6]`; AM: *&gamma;*~23~&nbsp;=&nbsp;`r pretty_fixed_effects[15,3]`, SE =&nbsp;`r pretty_fixed_effects[15,4]`. *t* = `r pretty_fixed_effects[15,5]`, *p* = `r pretty_fixed_effects[15,6]`; AE: *&gamma;*~33~&nbsp;=&nbsp;`r pretty_fixed_effects[16,3]`, SE =&nbsp;`r pretty_fixed_effects[16,4]`. *t* = `r pretty_fixed_effects[16,5]`, *p* = `r pretty_fixed_effects[16,6]`; AM: *&gamma;*~04~&nbsp;=&nbsp;`r pretty_fixed_effects[17,3]`, SE =&nbsp;`r pretty_fixed_effects[17,4]`. *t* = `r pretty_fixed_effects[17,5]`, *p* = `r pretty_fixed_effects[17,6]`) that indicates that the quadratic curve was more bowed for the L2 speakers, reflecting that all L2 groups predicted later than SS.

Keeping the term interactions also yielded a more complex interaction effect in the quadratic term between AE and lexical stress (*&gamma;*~36~&nbsp;=&nbsp;`r pretty_fixed_effects[30,3]`, SE =&nbsp;`r pretty_fixed_effects[30,4]`. *t* = `r pretty_fixed_effects[30,5]`, *p* = `r pretty_fixed_effects[30,6]`) and between AM and lexical stress (GroupAM x Lexical stress: *&gamma;*~00~&nbsp;=&nbsp;`r pretty_fixed_effects[31,3]`, SE =&nbsp;`r pretty_fixed_effects[31,4]`. *t* = `r pretty_fixed_effects[31,5]`, *p* = `r pretty_fixed_effects[31,6]`). 
This interaction shows that advanced L2 learners fixated more on the target in the preterit tense than they did in the present tense (see Fig. 4).
This increased number of fixations reveals that preterit tense may be easier to anticipate than present tense.
Figure 4 reflects the anticipation abilities difference in the advanced groups in the preterit tense towards the present tense. This difference consists of earlier increased fixations on the target verb in the preterit tense upon hearing a lexically unstressed syllable and is represented in the figure by the shift of the preterit tense line to the left in comparison to the present tense line.

Pairwise comparisons analyze performance across L2 groups. 
The pairwise comparisons are in Appendices 4 (advanced groups), 5 (intermediate groups), 6 (English groups) and 7 (Mandarin groups).
Comparing speakers of the same L1 across proficiency, there is only a difference in the quadratic term for the L1 English speakers (*&gamma;*~19~&nbsp;=&nbsp;`r pretty_pairwise_table_en[6,3]`, SE =&nbsp;`r pretty_pairwise_table_en[6,4]`. *t* = `r pretty_pairwise_table_en[6,5]`, *p* = `r pretty_pairwise_table_en[6,6]`), such that IE anticipate less than AE in the preterit tense.
As for L1 Mandarin Chinese speakers, there is only an effect on the intercept, where IM is shown to predict less than AM averaging across time course and stress conditions (*&gamma;*~08~&nbsp;=&nbsp;`r pretty_pairwise_table_ma[1,3]`, SE =&nbsp;`r pretty_pairwise_table_ma[1,4]`. *t* = `r pretty_pairwise_table_ma[1,5]`, *p* = `r pretty_pairwise_table_ma[1,6]`). 
That is, AM predict better overall than IM.
Comparing speakers of different L1s with similar proficiency, there was a significant effect on the intercept between IE and IM, such that IE had a higher fixation rate on the target than IM, indicating higher prediction in IE (*&gamma;*~08~&nbsp;=&nbsp;`r pretty_pairwise_table_int[1,3]`, SE =&nbsp;`r pretty_pairwise_table_int[1,4]`. *t* = `r pretty_pairwise_table_int[1,5]`, *p* = `r pretty_pairwise_table_int[1,6]`). 
At advanced proficiency, there was an effect of group on the linear term, demonstrating that AM increased their fixations on the target less steeply than AE in both stress conditions (`r pretty_pairwise_table_adv[2,3]`, SE =&nbsp;`r pretty_pairwise_table_adv[2,4]`. *t* = `r pretty_pairwise_table_adv[2,5]`, *p* = `r pretty_pairwise_table_adv[2,6]`).

The data in this study revealed that all groups except IM anticipated.
SS was the group that anticipated most and the earliest.
Within-group performance was similar across tense conditions for the intermediate groups and SS. 
For both advanced groups, preterit tense was easier to anticipate than present. 
Over proficiency, Mandarin speakers improved their prediction ability; English speakers improved overall although the anticipation performance difference is smaller.