---
title             : "The title"
shorttitle        : "Title"

author: 
  - name          : ""
    affiliation   : ""
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "my@email.com"
  - name          : ""
    affiliation   : ""

affiliation:
  - id            : ""
    institution   : ""
    
floatsintext      : yes
figurelist        : yes
tablelist         : yes
footnotelist      : yes
linenumbers       : yes
mask              : yes
draft             : yes

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_word
---

```{r setup, include = FALSE, warning = FALSE}
library("papaja")
library("officer")
library("flextable")
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

```{r, 'source-scripts-models', include = FALSE}
source(here::here("scripts", "02_load_data.R"))
source(here::here("scripts", "01_helpers.R"))

# Get path to saved models
gca_mods_path  <- here("mods", "stress", "gca")
glmm_mods_path  <- here("mods", "stress", "glmm")

# Load models as list and store full mod to global env
load(paste0(gca_mods_path, "/gca_mon_mods.Rdata"))
load(paste0(gca_mods_path, "/gca_l2_mods.Rdata"))
load(paste0(gca_mods_path, "/model_preds.Rdata"))
mon_preds <- readRDS(file = here("mods", "stress", "gca", "model_preds_mon.Rdata"))
load(paste0(gca_mods_path, "/nested_model_comparisons.Rdata"))

mon_onset_v1_final <- readRDS(here("mods", "stress", "glmm", "onset_v1", "mon_onset_v1_final.rds"))
l2_onset_c3_dele <- readRDS(here("mods", "stress", "glmm", "onset_c3", "l2_onset_c3_dele_final_z.rds"))
l2_onset_c3_dele <- readRDS(here("mods", "stress", "glmm", "onset_c3", "l2_onset_c3_dele_final_z.rds"))

```






# Journal of Memory and Language article (stress, natives and late advanced and intermediate EN y Ma Ch)

## Overview

This document contains updates to the statistical analysis for L1 transfer, L2 proficiency and L2 use on stress-suffix prediction. 
Last updated on `r Sys.Date()`. 
The results section can be copied and pasted into the corresponding google doc. 
The tables can also be copy and pasted where appropriate. 



## Statistical analysis
Statistical analyses were conducted on R (R Core Team, 2019) using the packages *lme4* (D. Bates, Mächler, Bolker, & Walker, 2014) and *multcomp* (Hothorn et al., 2016). 
The gaze-fixation data was downsampled to 10 ms and 50 ms bins. 
The 50 ms bins data were modeled using a growth curve analysis (GCA, Mirman, 2016) to observe how the pattern of gaze fixations changed over time, including linear, quadratic, and cubic orthogonal polynomials.
We centered the data at 200 ms after the onset of the last syllable of the target items to account for the time it takes to plan and launch a saccade (e.g., Fischer, 1992; Saslow, 1967). 
The empirical logit transformation was applied to binary responses (fixations on target or distractor, Barr, 2008). 
The 10 ms bins data were model using generalized linear mixed models (GLMM) at 200 ms after word target onset, onset of each segment in the target syllable, and onset of the suffix syllable to analyze the specific effect of each fixed effect on prediction and to find out precisely when each population started to anticipate.
For both the GCA and the GLMMs we first ran a model for the monolingual speakers with lexical stress as fixed effect and participant and item as random effects. 
For the L2 speakers, we ran two GCA and two GLMM at each time stamp of interest.
The first model of each kind included L1, lexical stress, and proficiency as fixed effects. 
The second one included L1, lexical stress, and L2 use as fixed effects. 
L1 was categorical, stood for transfer and was sum-coded. 
Lexical stress was categorical and was sum-coded. 
Proficiency and language use were continuous and standarized to z-scores. 
By-subject and by-item random effects were tested in all models. 
Nested model comparisons were implemented to assess main effects and interactions.

# 4. Results
The time course data for the three L1 populations are shown in Figure 3. 
The time courses reveal that gaze fixations on the target increased over time.
The three L1s fixated on the target at chance from the beginning of the sentence and increased fixations on the target before the offset of the target syllable.
Monolingual Spanish speakers (SS) increased gaze fixations on the target earlier than L2 speakers.
The fixations increase plateaued shortly after target syllable offset.

```{r, 'plot-time-course', echo=FALSE, fig.cap="Figure 3. Gaze fixation patterns on target from 500 ms before target syllable offset to 1000 ms after as a function of L1 and stress condition."}
knitr::include_graphics(
  here("figs", "stress", "gca", "stress_l1.png")
)
```


The summaries for the final models of the GCA are in the Appendices 2 (SS), 3 and 4 (L2).
The GCA models estimated the probability of gaze fixations on the target at the offset of the first syllable in the verb; the probabilities were estimated for each L1 population in both lexical stress conditions (paroxytone form = present, oxytone form = preterit) in comparison to a 50% fixation chance.
<!--The probabilities are contained in Tables 1 and .-->
The results for SS are presented first.
For the L2 speakers, the results for proficiency are presented first and results for L2 use last.

```{r, 'write-up-prep-mon', warning=F, eval=T}
# Prepare table to support easy in-line printing of equations

params <- gca_mon_mods$gca_mod_mon_base %>% 
  tidy_lme4() %>% 
  rename(B = Estimate)

params$subscript <- 
  c(paste0(0:3, 0)) 

params <- tibble::column_to_rownames(params, 'subscript')

params$subscript <- 
  c(paste0(0:3, 0)) 

# Shortcut for inline reporting from the above table
report_row <- function(row_name) report_fixef_row(params, row_name)

# # Pre-calculate intercept as proportion
# b0 <- params$B[params$subscript == "00"] %>% as.numeric
# b0_prop <- b0 %>% inv_logit %>% round(2) %>% remove_leading_zero

```


We conducted a GCA on SS to take them as reference when discussing our findings.
The model intercept for SS estimates their log odds for gaze fixation on the target averaging across lexical stress condition at `r report_row('1')`.
There were main effects in the linear (`r report_row('2')`), quadratic (`r report_row('3')`) and cubic polynomial time terms (`r report_row('4')`).
These results suggest SS were predicting the verb form upon hearing a stressed or unstressed syllable.
The fixation probability estimate of SS for both stress conditions is 0.953 (LB = 0.942; UB = 0.962).
Figure 4 shows the GCA model fit for SS.

```{r, 'plot-preds-mon', echo=FALSE, fig.cap="Figure 4. Growth curve analysis estimates of fixations on target as a function of lexical stress for the Spanish monolingual speakers during the analysis window. Lines represent model estimates, and the transparent ribbons represent ±SE. Empirical logit values on y-axis correspond to proportions of 0.12, 0.50, 0.88, and 0.98. The horizontal dotted line represents the 50% probability of fixating on the targets. The vertical dotted line indicates 200 ms after the offset of the target syllable."}
knitr::include_graphics(
  here("figs", "stress", "gca", "stress_mon.png")
)
```


Given the near ceiling effect in SS, we performed post-hoc GLMMs at the onset of every segment in the target syllable to find out when SS started anticipating.
We started at the onset of the verb.
The intercept log odds estimate for SS at verb onset was <em>&gamma;</em>&nbsp;=&nbsp;-0.138 (*p*&nbsp;&lt;&nbsp;0.467), indicating SS were at chance level and nothing so far was cueing them towards one tense or the other.
At the onset of the vowel in the target syllable, the log odds estimate was <em>&gamma;</em>&nbsp;=&nbsp;0.402, *SE* =  0.189, *z* = -0.727, *p*&nbsp;&lt;&nbsp;0.031, demonstrating SS were already predicting (see Table 0 for all fixed effects).
<!-- This result suggests there is some acoustic cue that seeps into the consonant that allows SS to start anticipating only by hearing that segment, as could be intensity. -->

```{r, warning=F}

# Get full mod and make it pretty for the table
mon_onset_v1_final %>%  
  tidy_lme4() %>% 
  mutate(Parameter = fix_param_names(Parameter)) %>%
  mutate_each(funs(format_fixef_num), Estimate:t) %>% 
  rename(`_t_` = t, `_p_` = p.value) %>%
  select(-p, -effect) %>%
  knitr::kable(format = "pandoc", align = str_tokenize("lrrrr")) 
```
*Table 0*. GLMM for Spanish speakers at onset of vowel in target syllable.


Two GCA analyses were conducted for the L2 groups.
One tested L2 proficiency along with L1 and stress condition.
The other one tested L2 use instead.
In both models, English speakers and present tense (paroxytone stress) are the baseline.

```{r, 'write-up-prep-dele', warning=F, eval=T}
# Prepare table to support easy in-line printing of equations
# params <- pretty_fixed_effects %>% 
#  rename(B = Estimate)

params <- gca_l2_mods$gca_l2_mod_dele_final %>%
  tidy_lme4() %>% 
  rename(B = Estimate)

params$subscript <- 
  c(paste0(0:5, 0), paste0(0:4, 1))

params <- tibble::column_to_rownames(params, 'subscript')

params$subscript <- 
  c(paste0(0:5, 0), paste0(0:4, 1))

# Shortcut for inline reporting from the above table
report_row <- function(row_name) report_fixef_row(params, row_name)

```

```{r, warning=F}

# Get full mod and make it pretty for the table
pretty_fixed_effects <- gca_l2_mods$gca_l2_mod_dele_final %>%  
  tidy_lme4() %>% 
  mutate(p = format_pval(p), 
         Parameter = fix_param_names(Parameter)) %>% 
  mutate_each(funs(format_fixef_num), Estimate:t) %>% 
  rename(`_t_` = t, `_p_` = p) 

# Include gammas (Gij) after each parameter name
subs <- c(paste0(0:3, 0), paste0(0:3, 1), 
          paste0(0:2, 2))
var_labels <- parenthesize(paste0(emphasize("&gamma;"), "~", subs, "~"))
pretty_fixed_effects$Parameter %<>% paste(., var_labels)

pretty_fixed_effects %>% 
  select(-effect) %>%
  knitr::kable(format = "pandoc", align = str_tokenize("lrrrr")) 

```

Table 1: Growth curve model fixed effects for L2 speakers (proficiency).


The GCA with proficiency as a predictor estimates the intercept log odds at `r report_row(1)`.
The linear (`r report_row(2)`), quadratic (`r report_row(3)`) and cubic (`r report_row(4)`) polynomial time terms estimates reached significance.
These results suggest the English speakers were anticipating present tense at target syllable offset.
The absence of main effects from L1 (<em>&chi^2^;</em>&nbsp;(1) = 2.840, *p* = 0.092) and stress condition (<em>&chi^2^;</em>&nbsp;(1) = 0.570, *p* = 0.450) suggest that they were also anticipating preterit tense and that Mandarin speakers were also anticipating both tenses.
<!--These results suggest the L2 speakers were anticipating both tenses at target syllable offset, regardless of their L1.-->
Adding proficiency resulted in a main effect of proficiency (<em>&chi^2^;</em>&nbsp;(1) = 7.523, *p* = 0.006), such that the higher the L2 proficiency, the higher the likelihood of predicting (`r report_row(5)`).
The variability in prediction probability as a function of proficiency is shown in Table 2.
The values under the Proficiency column refer to the minimum and maximum scores obtained within each L1 as converted to z-scores.
As Table 2 shows, the higher the proficiency, the higher the probability of fixating on the target at target syllable offset.

```{r, table-dele-probs, eval=T, echo=F}

border_1 <- fp_border(width = 1.5)
border_2 <- fp_border(width = 0.75)

model_preds$target_offset_preds_l2_dele %>% 
  mutate(stress = if_else(stress == 1, "Present", "Preterit"),
         l1 = if_else(l1 == 'en', "English", "Mandarin"),
         l1 = fct_relevel(l1, "English", "Mandarin")) %>% 
  arrange(l1, stress) %>% 
  group_by(l1, stress) %>%
  filter(., DELE == max(DELE) | DELE == min(DELE)) %>%
  distinct() %>%
  #ungroup() %>%
  mutate(l1 = blank_same_as_last(as.character(l1)),
         stress = blank_same_as_last(as.character(stress))) %>%
  select(L1 = l1, `Lexical stress` = stress, Proficiency = DELE, Probability = prob,
         LB = prob_lb, UB = prob_ub) %>%
  flextable() %>% 
  width(., j = c(2, 3, 4), width = c(1.1, 1.3, 1.1)) %>%
  font(., fontname = "Times", part = "all") %>%
  fontsize(., size = 11) %>% 
  border_remove(.) %>%  
  border(., part = "header", 
            border.top = border_1,
            border.bottom = border_2) %>% 
  hline_bottom(., part = "body", border = border_1)
```

*Table 2*: Model estimates for probability of target fixations ±SE at 200 ms after the target syllable offset as a function of L2 proficiency. (LB = lower bound; UP = upper bound).


The estimates also show interaction effects between proficiency x stress in the English speakers in the linear time term (`r report_row(8)`) and the quadratic term (`r report_row(10)`).
These two interactions suggest that the influence of proficiency varied according to stress pattern in English speakers.
In the present tense, when the stress pattern was paroxytone, proficiency played barely any role, as shown on the top left panel of Figure 5.
In the preterit tense, with an oxytone pattern, speakers with higher proficiency were likelier to predict and did so earlier.

```{r, 'plot-preds-dele-split', echo=FALSE, fig.cap="Figure 5. Growth curve analysis estimates of fixations on target as a function of lexical stress for each L2 group during the analysis window. Lines represent model estimates, and the transparent ribbons represent ±SE. Empirical logit values on y-axis correspond to proportions of 0.12, 0.50, 0.88, and 0.98. The horizontal dotted line represents the 50% probability of fixating on the targets. The vertical dotted line indicates 200 ms after the offset of the target syllable."}
knitr::include_graphics(
  here("figs", "stress", "gca", "stress_dele_split.png")
)
```



```{r, 'write-up-prep-use', warning=F, eval=T}
# Prepare table to support easy in-line printing of equations
# params <- pretty_fixed_effects %>% 
#  rename(B = Estimate)

params <- gca_l2_mods$gca_l2_mod_use_final %>%
  tidy_lme4() %>% 
  rename(B = Estimate)

params$subscript <- 
  c(paste0(0:4, 0), paste0(0:4, 1),
    paste0(0:0, 2))

params <- tibble::column_to_rownames(params, 'subscript')

params$subscript <- 
  c(paste0(0:4, 0), paste0(0:4, 1), 
    paste0(0:0, 2))

# Shortcut for inline reporting from the above table
report_row <- function(row_name) report_fixef_row(params, row_name)

```


```{r, warning=F}

# Get full mod and make it pretty for the table
pretty_fixed_effects <- gca_l2_mods$gca_l2_mod_use_final %>%  
  tidy_lme4() %>% 
  mutate(p = format_pval(p), 
         Parameter = fix_param_names(Parameter)) %>% 
  mutate_each(funs(format_fixef_num), Estimate:t) %>% 
  rename(`_t_` = t, `_p_` = p) 

# Include gammas (Gij) after each parameter name
subs <- c(paste0(0:3, 0), paste0(0:3, 1), 
          paste0(0:2, 2))
var_labels <- parenthesize(paste0(emphasize("&gamma;"), "~", subs, "~"))
pretty_fixed_effects$Parameter %<>% paste(., var_labels)

pretty_fixed_effects %>% 
  select(-effect) %>%
  knitr::kable(format = "pandoc", align = str_tokenize("lrrrr")) 

```

*Table 3*: Growth curve model fixed effects for L2 speakers (L2 use)

The GCA analysis with L2 weekly use in percentage estimates the intercept log odds at `r report_row(1)` for the L2 speakers.
There estimates of the linear (`r report_row(2)`), quadratic (`r report_row(3)`) and cubic (`r report_row(4)`) polynomial time terms were significant.
These results suggest again the L2 speakers were anticipating tense at target syllable offset.
There was an effect of L2 use in the quadratic polynomial time term (<em>&chi^2^;</em>&nbsp;(1) = 4.750, *p* = 0.029), such that the more frequent the use, the higher the likelihood of predicting (`r report_row(7)`).
The probabilities of fixating as a function of L2 use can be seen in Table 4.
The two values in the column Weekly L2 % use represent the minimum and the maximum L2 use reported by the participants.
As Table 4 shows, the more frequent the weekly L2 use, the greater the probability of prediction. 


```{r, table-use-probs, eval=T, echo=F}

border_1 <- fp_border(width = 1.5)
border_2 <- fp_border(width = 0.75)

model_preds$target_offset_preds_l2_use %>% 
  mutate(stress = if_else(stress == 1, "Present", "Preterit"),
         l1 = if_else(l1 == 'EN', "English", "Mandarin"),
         l1 = fct_relevel(l1, "English", "Mandarin")) %>% 
  group_by(l1, stress) %>%
  filter(., percent_l2_week == max(percent_l2_week) | 
           percent_l2_week == min(percent_l2_week)) %>%
  distinct() %>%
  # ungroup() %>%
  arrange(l1, stress) %>% 
  mutate(l1 = blank_same_as_last(as.character(l1)),
         stress = blank_same_as_last(as.character(stress))) %>%
  select(L1 = l1, `Lexical stress` = stress, `Weekly L2 % use` = percent_l2_week, Probability = prob,
         LB = prob_lb, UB = prob_ub) %>%
  flextable() %>% 
  width(., j = c(2, 3, 4), width = c(1.1, 1.3, 1.1)) %>%
  font(., fontname = "Times", part = "all") %>%
  fontsize(., size = 11) %>% 
  border_remove(.) %>%  
  border(., part = "header", 
            border.top = border_1,
            border.bottom = border_2) %>% 
  hline_bottom(., part = "body", border = border_1)
```

*Table 4*: Model estimates for probability of target fixations ±SE at 200 ms 
after the target syllable offset as a function of L2 weekly % use. (LB = lower bound; UP = upper bound).


There was an interaction effect of L2 use x stress in the linear term for the Mandarin speakers (<em>&chi^2^;</em>&nbsp;(2) = 13.409, *p* = 0.001).
This interaction resulted in a negative estimate indicating that the slope for the present tense predictions is generally steeper (`r report_row(7)`), which suggests speakers of use L2 more often in a week anticipate faster.
The steeper slope can be observed in Figure 6.

```{r, 'plot-preds-use-split', echo=FALSE, fig.cap="Figure 6. Growth curve analysis estimates of fixations on target as a function of lexical stress and L2 weekly use for each L2 group during the analysis window. Lines represent model estimates, and the transparent ribbons represent ±SE. Empirical logit values on y-axis correspond to proportions of 0.12, 0.50, 0.88, and 0.98. The horizontal dotted line represents the 50% probability of fixating on the targets. The vertical dotted line indicates 200 ms after the offset of the target syllable."}
knitr::include_graphics(
  here("figs", "stress", "gca", "stress_use_l1.png")
)
```

The interaction effect of L2 use x stress in the linear term also caused differences by group (English: `r report_row(10)`; Mandarin: `r report_row(11)`)
This interaction suggests that the beneficial effects of increased L2 use had a greater impact in the present tense, as Figure 7 shows, by helping speakers anticipate faster.

```{r, 'plot-preds-use-split', echo=FALSE, fig.cap="Figure 7. Growth curve analysis estimates of fixations on target as a function of lexical stress and weekly L2 use for each stress condition during the analysis window. Lines represent model estimates, and the transparent ribbons represent ±SE. Empirical logit values on y-axis correspond to proportions of 0.12, 0.50, 0.88, and 0.98. The horizontal dotted line represents the 50% probability of fixating on the targets. The vertical dotted line indicates 200 ms after the offset of the target syllable."}
knitr::include_graphics(
  here("figs", "stress", "gca", "stress_use_cond.png")
)
```



Following the same procedure as for SS, we conducted post-hoc GLMMs to find out when the L2 speakers started to anticipate (see Tables 5 and 6).
For the GLMMs, we also ran two nested comparison models at each time stamp of interest (onset of target word, and then onset of each segment in the first syllable and onset of second syllable).
One of them included proficiency as fixed effect and the other one included L2 use.
As a reminder, the baselines are present tense and L1 English speakers.


```{r, warning=F}

# Get full mod and make it pretty for the table
l2_onset_c3_dele %>%  
  tidy_lme4() %>% 
  mutate(Parameter = fix_param_names(Parameter)) %>%
  mutate_each(funs(format_fixef_num), Estimate:t) %>% 
  rename(`_t_` = t, `_p_` = p.value) %>%
  select(-p, -effect) %>%
  knitr::kable(format = "pandoc", align = str_tokenize("lrrrr")) 

```

*Table 5*. GLMM with proficiency for L2 speakers at onset of second syllable.


```{r, warning=F}

# Get full mod and make it pretty for the table
l2_onset_c3_use %>%  
  tidy_lme4() %>% 
  mutate(Parameter = fix_param_names(Parameter)) %>%
  mutate_each(funs(format_fixef_num), Estimate:t) %>% 
  rename(`_t_` = t, `_p_` = p.value) %>%
  select(-p, -effect) %>%
  knitr::kable(format = "pandoc", align = str_tokenize("lrrrr")) 

```

*Table 2*. GLMM for L2 speakers with weekly L2 use at onset of second syllable.



In contrast to SS, L2 speakers only showed signs of anticipation at the onset of the second syllable.
At this time stamp, the log odd intercept estimates were significant for the first time in both L2 models: with proficiency <em>&beta;</em>&nbsp;=&nbsp;1.137, *SE* = 0.123, *z* = 9.239, *p* = 0.000; with L2 use <em>&beta;</em>&nbsp;=&nbsp;1.142, *SE* = 0.130, *z* = 8.781, *p* = 0.000. 
<!--This delay in comparison to SS indicates L2 speakers need more information to generate verb tense suffix predictions.
While SS do not seem to need lexical stress information, this piece of information is crucial for L2 speakers to generate the prediction.-->
While no L1 main effects were observed in the GCA models, the GLMMs run to analyze the influence of predictors in more detail did show a difference between L2 groups (<em>&chi^2^;</em>&nbsp;(1) = 3.894, *p* = 0.048).
The specific estimates for each model, one when L2 proficiency was considered (<em>&beta;</em>&nbsp;=&nbsp;-0.304, *SE* = 0.136, *z* = -2.238, *p* = .025)  and the other when L2 use was included , follow a similar trend.
In the proficiency model, there was a main effect of L1 (<em>&beta;</em>&nbsp;=&nbsp;-0.352, *SE* = 0.142, *z* = -2.484, *p* = .013), such that Mandarin speakers anticipated less than English speakers.
There was also a main effect of proficiency (<em>&chi^2^;</em>&nbsp;(1) = 11.681, *p* = 0.001), in that higher proficiency correlated with increased anticipation (<em>&gamma;</em>&nbsp;=&nbsp;0.298, *SE* = 0.085, *z* = 3.496, *p* = .000).
These values in the proficiency model indicate that Mandarin speakers were anticipating less than English speakers, and that proficiency mediated ability to anticipate in both populations, with more proficient individuals generating predictions more consistently.
In the L2 use model, there was a main effect L2 use (<em>&chi^2^;</em>&nbsp;(1) = 5.792, *p* = 0.016), pointing that greater L2 use correlated with better anticipation <em>&beta;</em>&nbsp;=&nbsp;0.236, *SE* = 0.097, *z* = 2.435, *p* = 0.015.

In summary, the data in this study revealed that all groups were anticipating tense suffixes at the offset of the target syllable.
SS started anticipating in the first consonant of the verb, which suggests they are relying on cues other than lexical stress to generate tense suffix predictions.
L2 speakers needed to hear the target syllable to generate predictions, which suggests they were using lexical stress as a cue.
English speakers were more successful in their prediction than Mandarin speakers. 
Proficiency and L2 use mediated L2 speakers' ability to generate predictions.








# Other plots






# Tables 

## Model estimates at target syllable offset  

```{r, table-target-offset-props, eval=T, echo=F}

border_1 <- fp_border(width = 1.5)
border_2 <- fp_border(width = 0.75)

mon_preds %>% 
  mutate(cond = if_else(stress == 1, "Present", "Preterit")) %>% 
  # arrange(cond, ospan) %>% 
  arrange(cond) %>%
  group_by(cond) %>%
  mutate(prob = mean(prob),
         prob_lb = mean(prob_lb),
         prob_ub = mean(prob_ub)) %>%
  mutate(cond = blank_same_as_last(as.character(cond))) %>%
  # group_by(cond) %>%
  # filter(., ospan == max(ospan) |
  #          ospan == min(ospan)) %>%
  # ungroup() %>%
  select(`Lexical stress` = cond, Probability = prob, #ospan, 
         LB = prob_lb, UB = prob_ub) %>%
  distinct() %>%
  flextable() %>% 
  #width(., j = c(2, 3, 4), width = c(1.1, 1.3, 1.1)) %>% 
  font(., fontname = "Times", part = "all") %>%
  fontsize(., size = 11) %>% 
  border_remove(.) %>%  
  border(., part = "header", 
            border.top = border_1,
            border.bottom = border_2) %>% 
  hline_bottom(., part = "body", border = border_1)
```
*Table 1*: Model estimates for probability of target fixations in monolinguals ±SE at 200 ms 
after the target syllable offset. (LB = lower bound; UP = upper bound).

## Fixed effects

```{r, warning=F}

# Get full mod and make it pretty for the table
pretty_fixed_effects <- gca_mon_mods$gca_mod_mon_base %>% 
  tidy_lme4() %>% 
  mutate(p = format_pval(p), 
         Parameter = fix_param_names(Parameter)) %>% 
  mutate_each(funs(format_fixef_num), Estimate:t) %>% 
  rename(`_t_` = t, `_p_` = p) 

# Include gammas (Gij) after each parameter name
subs <- c(paste0(0:3, 0))
var_labels <- parenthesize(paste0(emphasize("&gamma;"), "~", subs, "~"))
pretty_fixed_effects$Parameter %<>% paste(., var_labels)

# pretty_fixed_effects <- pretty_fixed_effects[0:4,]

pretty_fixed_effects %>% 
  select(-effect) %>%
  knitr::kable(format = "pandoc", align = str_tokenize("lrrrr")) 

```

Appendix 2. Growth Curve Analysis fixed effects (monolinguals)








```{r, warning=F}

# # Get full mod and make it pretty for the table
# pretty_fixed_effects <- gca_l2_mod_wm_final %>%  #gca_l2_mods$
#   tidy_lme4() %>% 
#   mutate(p = format_pval(p), 
#          Parameter = fix_param_names(Parameter)) %>% 
#   mutate_each(funs(format_fixef_num), Estimate:t) %>% 
#   rename(`_t_` = t, `_p_` = p) 
# 
# # Include gammas (Gij) after each parameter name
# subs <- c(paste0(0:3, 0), paste0(0:3, 1), 
#           paste0(0:3, 2))
# var_labels <- parenthesize(paste0(emphasize("&gamma;"), "~", subs, "~"))
# pretty_fixed_effects$Parameter %<>% paste(., var_labels)
# 
# pretty_fixed_effects %>% 
#   knitr::kable(format = "pandoc", align = str_tokenize("lrrrr")) 

```

Appendix 0: Growth curve model fixed effects L2 (WM)


## Random effects

```{r, 'ranef-table-mon', results = "asis"}
ranef_table <- gca_mon_mods$gca_mod_mon_base %>% 
  tidy_ranef_summary %>% 
  # Format the numbers
  mutate_each(funs(format_fixef_num), vcov, sdcor) %>%
  mutate_each(funs(format_cor), -var1, -grp, -vcov, -sdcor) %>%
  sort_ranef_grps %>%
  # Format variable names and group names
  mutate(var1 = fix_param_names(var1) %>% blank_nas,
         grp =  blank_same_as_last(grp) %>% fix_param_names) %>% 
  rename(Group = grp, Parameter = var1, Variance = vcov, SD = sdcor)

# Correlation columns need names with characters so that pandoc can align them
names(ranef_table)[5:9] <- 
  c("Correlations", "&nbsp;", " &nbsp;", "  &nbsp;", "  &nbsp;")

ranef_table %>% 
  knitr::kable(format = "pandoc", align = str_tokenize("llrrrrrr"))
```




Appendix 5.Growth curve model random effects (monolinguals)





```{r, 'ranef-table-l2', results = "asis"}
ranef_table <- gca_l2_mods$gca_l2_mod_use_final %>% # Ranef same for DELE and USE
  tidy_ranef_summary %>% 
  # Format the numbers
  mutate_each(funs(format_fixef_num), vcov, sdcor) %>%
  mutate_each(funs(format_cor), -var1, -grp, -vcov, -sdcor) %>%
  sort_ranef_grps %>%
  # Format variable names and group names
  mutate(var1 = fix_param_names(var1) %>% blank_nas,
         grp =  blank_same_as_last(grp) %>% fix_param_names) %>% 
  rename(Group = grp, Parameter = var1, Variance = vcov, SD = sdcor)

# Correlation columns need names with characters so that pandoc can align them
names(ranef_table)[5:9] <- 
  c("Correlations", "&nbsp;", " &nbsp;", "  &nbsp;", "  &nbsp;")

ranef_table %>% 
  knitr::kable(format = "pandoc", align = str_tokenize("llrrrrrr"))
```

Appendix 6: Growth curve model random effects (L2)


