---
title             : "The title"
shorttitle        : "Title"

author: 
  - name          : "Laura Fernandez Arroyo"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "my@email.com"
  - name          : "Nuria Sagarra"
    affiliation   : "1"
  - name          : "Cristina Lozano-Argüelles"
    affilitation  : "2"

affiliation:
  - id            : "1"
    institution   : "Rutgers University"
  - id            : "2"
    institution   : "John Jay College/CUNY"



keywords          : ""
wordcount         : ""



floatsintext      : yes
figurelist        : yes
tablelist         : yes
footnotelist      : yes
linenumbers       : yes
mask              : yes
draft             : yes

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_word
---

```{r setup, include = FALSE}
library("papaja")
library("officer")
library("flextable")
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

```{r, 'source-scripts-models'}
source(here::here("scripts", "02_load_data.R"))
source(here::here("scripts", "01_helpers.R"))

# Get path to saved models
gca_mods_path  <- here("mods", "stress", "gca")

# Load models as list and store full mod to global env
load(paste0(gca_mods_path, "/model_preds.Rdata"))
load(paste0(gca_mods_path, "/gca_full_mods.Rdata"))
load(paste0(gca_mods_path, "/nested_model_comparisons.Rdata"))

```






# Second Language Research article (stress, natives and late advanced and intermediate EN y Ma Ch

## Overview

This document contains updates to the statistical analysis for stress_unrelated experiment 
(draft for ISB). 
Last updated on `r Sys.Date()`. 
The results section can be copied and pasted into the corresponding google doc. 
The tables can also be copy and pasted where appropriate. 

## Main changes

**Participants**  



**Analyses**  










# Plots

```{r, 'plot-ind-preds', echo=FALSE, fig.cap="Growth curve analysis estimates of fixations on target as a function of lexical stress for each group during the analysis window. Lines represent model estimates, and the transparent ribbons represent ±SE. Empirical logit values on y-axis correspond to proportions of 0.12, 0.50, 0.88, and 0.98. The horizontal dotted line represents the 50% probability of fixating on the targets. The vertical dotted line indicates 200 ms. after the offset of the target syllable."}
knitr::include_graphics(
  here("figs", "stress", "gca", "stress_p2.png")
)
```

```{r, 'plot-group-preds', echo=FALSE, fig.cap="Growth curve analysis estimates of fixations on the target as a function of lexical stress for each group during the analysis window. Symbols and lines represent model estimates, and the ribbons represent ±SE. Empirical logit values on y-axis correspond to proportions of 0.12, 0.50, 0.88, and 0.98. The horizontal dotted line represents the 50% probability of fixating on the targets. The vertical dotted line indicates 200 ms. after the offset of the target syllable."}
knitr::include_graphics(
  here("figs", "stress", "gca", "stress_p3.png")
)
```













# Tables 

## Model estimates at target syllable offset  


```{r, table-target-offset-props, eval=T, echo=F}

border_1 <- fp_border(width = 1.5)
border_2 <- fp_border(width = 0.75)

model_preds$target_offset_preds %>% 
  mutate(cond = if_else(stress == 1, "present", "preterit"),
         group = fct_relevel(group, "SS", "AE", "AM", "IE", "IM")) %>% 
  arrange(group, desc(stress)) %>% 
  mutate(group = blank_same_as_last(as.character(group))) %>% 
  select(Group = group, `Lexical stress` = cond, Probability = prob, LB = prob_lb, 
         UB = prob_ub) %>% 
  flextable() %>% 
  width(., j = c(2, 3, 4), width = c(1.1, 1.3, 1.1)) %>% 
  font(., fontname = "Times", part = "all") %>%
  fontsize(., size = 11) %>% 
  border_remove(.) %>%  
  border(., part = "header", 
            border.top = border_1,
            border.bottom = border_2) %>% 
  hline_bottom(., part = "body", border = border_1)
```

*Table 1*: Model estimates for probability of target fixations ±SE at 200 ms 
after the target syllable offset. (LB = lower bound; UP = upper bound)




## Fixed effects

```{r, warning=F}

# Get full mod and make it pretty for the table
pretty_fixed_effects <- gca_full_mods$gca_full_mod_int_2 %>% 
  tidy_lme4() %>% 
  mutate(p = format_pval(p), 
         Parameter = fix_param_names(Parameter)) %>% 
  mutate_each(funs(format_fixef_num), Estimate:t) %>% 
  rename(`_t_` = t, `_p_` = p) 

# Include gammas (Gij) after each parameter name
subs <- c(paste0(0:3, 0), paste0(0:3, 1), 
          paste0(0:3, 2), paste0(0:3, 3), 
          paste0(0:3, 4), paste0(0:3, 5), 
          paste0(0:3, 6))
var_labels <- parenthesize(paste0(emphasize("&gamma;"), "~", subs, "~"))
pretty_fixed_effects$Parameter %<>% paste(., var_labels)

pretty_fixed_effects %>% 
  knitr::kable(format = "pandoc", align = str_tokenize("lrrrr")) 

```

Appendix 1: Growth curve model fixed effects






## Random effects

```{r, 'ranef-table', results = "asis"}
ranef_table <- gca_full_mods$gca_full_mod_int_2 %>% 
  tidy_ranef_summary %>% 
  # Format the numbers
  mutate_each(funs(format_fixef_num), vcov, sdcor) %>%
  mutate_each(funs(format_cor), -var1, -grp, -vcov, -sdcor) %>%
  sort_ranef_grps %>%
  # Format variable names and group names
  mutate(var1 = fix_param_names(var1) %>% blank_nas,
         grp =  blank_same_as_last(grp) %>% fix_param_names) %>% 
  rename(Group = grp, Parameter = var1, Variance = vcov, SD = sdcor)

# Correlation columns need names with characters so that pandoc can align them
names(ranef_table)[5:9] <- 
  c("Correlations", "&nbsp;", " &nbsp;", "  &nbsp;", "  &nbsp;")

ranef_table %>% 
  knitr::kable(format = "pandoc", align = str_tokenize("llrrrrrr"))
```

Appendix 2: Growth curve model random effects




## Pairwise comparisons

```{r, 'learner-comparison-adv'}
########  AES and AMS 

# make table for printing
pairwise_comp_adv <- gca_full_mods$gca_full_mod_int_2_aes %>% 
  tidy_lme4 %>% 
  rename(B = Estimate) %>% 
  filter(str_detect(Parameter, "ams") == TRUE) 

# Add subscript column, convert to rownames, and then add it again
pairwise_comp_adv$subscript <- c(paste0(0:3, 8), paste0(0:1, 9))
pairwise_comp_adv <- tibble::column_to_rownames(pairwise_comp_adv, 'subscript')
pairwise_comp_adv$subscript <- c(paste0(0:3, 8), paste0(0:1, 9))


# Shortcut for inline reporting from the above table
report_pairwise <- function(row_name) report_fixef_row(pairwise_comp_adv, row_name)

```


```{r, pairwise-comp-table-adv, results='asis', eval=T}

# Make table for appendix
pretty_pairwise_table_adv <- gca_full_mods$gca_full_mod_int_2_aes %>% 
  tidy_lme4 %>% 
  mutate(p = format_pval(p), 
         Parameter = fix_param_names(Parameter)) %>% 
  mutate_each(funs(format_fixef_num), Estimate:t) %>% 
  rename(`_t_` = t, `_p_` = p) %>% 
  filter(str_detect(Parameter, "AM") == TRUE) 

pretty_pairwise_table_adv$Parameter %<>% str_replace("Group AE", "AE - AM")

# Include gammas after each parameter name
pw_subs <- c(paste0(0:3, 8), paste0(0:1, 9))
pw_var_labels <- parenthesize(paste0(emphasize("&gamma;"), "~", pw_subs, "~"))
pretty_pairwise_table_adv$Parameter %<>% paste(., pw_var_labels)

pretty_pairwise_table_adv %>% 
  knitr::kable(format = "pandoc", align = str_tokenize("lrrrr")) 

```

Appendix 3a: Pairwise comparisons between advanced learner groups (AE reference). 


```{r, 'learner-comparison_ch'}
########### AMS and IMS

# make table for printing
pairwise_comp_ch <- gca_full_mods$gca_full_mod_int_2_ams %>% 
  tidy_lme4 %>% 
  rename(B = Estimate) %>% 
  filter(str_detect(Parameter, "ims") == TRUE) 

# Add subscript column, convert to rownames, and then add it again
pairwise_comp_ch$subscript <- c(paste0(0:3, 8), paste0(0:1, 9))
pairwise_comp_ch <- tibble::column_to_rownames(pairwise_comp_ch, 'subscript')
pairwise_comp_ch$subscript <- c(paste0(0:3, 8), paste0(0:1, 9))


# Shortcut for inline reporting from the above table
report_pairwise_ch <- function(row_name) report_fixef_row(pairwise_comp_ch, row_name)

```


```{r, pairwise-comp-table-ch, results='asis', eval=T}

# Make table for appendix
pretty_pairwise_table_ma <- gca_full_mods$gca_full_mod_int_2_ams %>% 
  tidy_lme4 %>% 
  mutate(p = format_pval(p), 
         Parameter = fix_param_names(Parameter)) %>% 
  mutate_each(funs(format_fixef_num), Estimate:t) %>% 
  rename(`_t_` = t, `_p_` = p) %>% 
  filter(str_detect(Parameter, "IM") == TRUE) 

pretty_pairwise_table_ma$Parameter %<>% str_replace("Group AM", "AM - IM")

# Include gammas after each parameter name
pw_subs <- c(paste0(0:3, 8), paste0(0:1, 9))
pw_var_labels <- parenthesize(paste0(emphasize("&gamma;"), "~", pw_subs, "~"))
pretty_pairwise_table_ma$Parameter %<>% paste(., pw_var_labels)

pretty_pairwise_table_ma %>% 
  knitr::kable(format = "pandoc", align = str_tokenize("lrrrr")) 

```
Appendix 3b: Pairwise comparisons between Mandarin Chinese learner groups (AM reference).

```{r, 'learner-comparison-en'}
########### AES and IES

# make table for printing
pairwise_comp_en <- gca_full_mods$gca_full_mod_int_2_aes %>% 
  tidy_lme4 %>% 
  rename(B = Estimate) %>% 
  filter(str_detect(Parameter, "ies") == TRUE) 

# Add subscript column, convert to rownames, and then add it again
pairwise_comp_en$subscript <- c(paste0(0:3, 8), paste0(0:1, 9))
pairwise_comp_en <- tibble::column_to_rownames(pairwise_comp_en, 'subscript')
pairwise_comp_en$subscript <- c(paste0(0:3, 8), paste0(0:1, 9))


# Shortcut for inline reporting from the above table
report_pairwise <- function(row_name) report_fixef_row(pairwise_comp, row_name)

```


```{r, pairwise-comp-table-en, results='asis', eval=T}
# Make table for appendix
pretty_pairwise_table_en <- gca_full_mods$gca_full_mod_int_2_aes %>% 
  tidy_lme4 %>% 
  mutate(p = format_pval(p), 
         Parameter = fix_param_names(Parameter)) %>% 
  mutate_each(funs(format_fixef_num), Estimate:t) %>% 
  rename(`_t_` = t, `_p_` = p) %>% 
  filter(str_detect(Parameter, "IE") == TRUE) 

pretty_pairwise_table_en$Parameter %<>% str_replace("Group AE", "AE - IE")

# Include gammas after each parameter name
pw_subs <- c(paste0(0:3, 8), paste0(0:1, 9))
pw_var_labels <- parenthesize(paste0(emphasize("&gamma;"), "~", pw_subs, "~"))
pretty_pairwise_table_en$Parameter %<>% paste(., pw_var_labels)

pretty_pairwise_table_en %>% 
  knitr::kable(format = "pandoc", align = str_tokenize("lrrrr")) 

```
Appendix 3c: Pairwise comparisons between EN learners (AE reference).


```{r, 'learner-comparison-int'}
########### IES and IMS

# make table for printing
pairwise_comp_int <- gca_full_mods$gca_full_mod_int_2_ies %>% 
  tidy_lme4 %>% 
  rename(B = Estimate) %>% 
  filter(str_detect(Parameter, "ims") == TRUE) 

# Add subscript column, convert to rownames, and then add it again
pairwise_comp_int$subscript <- c(paste0(0:3, 8), paste0(0:1, 9))
pairwise_comp_int <- tibble::column_to_rownames(pairwise_comp_int, 'subscript')
pairwise_comp_int$subscript <- c(paste0(0:3, 8), paste0(0:1, 9))


# Shortcut for inline reporting from the above table
report_pairwise <- function(row_name) report_fixef_row(pairwise_comp_int, row_name)

```


```{r, pairwise-comp-table-int, results='asis', eval=T}
# Make table for appendix
pretty_pairwise_table_int <- gca_full_mods$gca_full_mod_int_2_ies %>% 
  tidy_lme4 %>% 
  mutate(p = format_pval(p), 
         Parameter = fix_param_names(Parameter)) %>% 
  mutate_each(funs(format_fixef_num), Estimate:t) %>% 
  rename(`_t_` = t, `_p_` = p) %>% 
  filter(str_detect(Parameter, "IM") == TRUE) 

pretty_pairwise_table_int$Parameter %<>% str_replace("Group IE", "IE - IM")

# Include gammas after each parameter name
pw_subs <- c(paste0(0:3, 8), paste0(0:1, 9))
pw_var_labels <- parenthesize(paste0(emphasize("&gamma;"), "~", pw_subs, "~"))
pretty_pairwise_table_int$Parameter %<>% paste(., pw_var_labels)

pretty_pairwise_table_int %>% 
  knitr::kable(format = "pandoc", align = str_tokenize("lrrrr")) 

```
Appendix 3d: Pairwise comparisons between intermediate learner groups (IE reference).





# 5. Results

```{r, 'write-up-prep', warning=F, eval=T}
# Prepare table to support easy in-line printing of equations
# params <- pretty_fixed_effects %>% 
#  rename(B = Estimate)

params <- gca_full_mods$gca_full_mod_int_2 %>% 
  tidy_lme4() %>% 
  rename(B = Estimate)

params$subscript <- 
  c(paste0(0:4, 0), paste0(0:4, 1), 
    paste0(0:4, 2), paste0(0:3, 3), 
    paste0(0:3, 4), paste0(0:3, 5), 
    paste0(0:3, 6))

params <- tibble::column_to_rownames(params, 'subscript')

params$subscript <- 
  c(paste0(0:4, 0), paste0(0:4, 1), 
    paste0(0:4, 2), paste0(0:3, 3), 
    paste0(0:3, 4), paste0(0:3, 5), 
    paste0(0:3, 6))

# Shortcut for inline reporting from the above table
report_row <- function(row_name) report_fixef_row(params, row_name)

# Pre-calculate intercept as proportion
b0 <- params$B[params$subscript == "00"] %>% as.numeric
b0_prop <- b0 %>% inv_logit %>% round(2) %>% remove_leading_zero

```



The summary for the full model of the Growth Curve Analysis is in the Appendices 2 and 3, and the results are plotted in Figures 3 and 4. 
In the plots, the x-axis in these plots represents time (ms.) in the trial and the y-axis represents the logit probability of fixation on the target. 
Figure 3 represents the model fit for each group in both conditions. 
Figure 4 represents the model fit for each verbal tense across groups. 
The vertical line at 200 ms. represents the offset of the first syllable in the target verbs.

These plots indicate that SS start anticipating earlier than the L2 groups. 
The higher crossing point of the 200 ms. line also indicates that they are anticipating more than the L2 groups. 
Within groups, SS, IE and to some extent IM anticipate present and preterit tense similarly. 
In the case of AE and AM, preterit tense appears to be easier to anticipate than present tense.

For reporting the results of the growth curve model, SS and present tense were taken as baseline. 
The results for these speakers are presented first.
Comparisons between L2 groups according to L1 and to L2 proficiency come afterwards.
The model intercept estimates the log odds of SS fixating their gaze on the target averaging across lexical stress condition and time course (*&gamma;*~00~&nbsp;=&nbsp;`r pretty_fixed_effects[1,3]`, SE =&nbsp;`r pretty_fixed_effects[1,4]`. *t* = `r pretty_fixed_effects[1,5]`, *p* = `r pretty_fixed_effects[1,6]`). 
This value for the intercept suggests that SS were anticipating correctly. 
The linear and cubic polynomial time terms captured the sigmoid shape of the time course and were retained in the model (*&gamma;*~10~&nbsp;=&nbsp;`r pretty_fixed_effects[2,3]`, SE =&nbsp;`r pretty_fixed_effects[2,4]`. *t* = `r pretty_fixed_effects[2,5]`, *p* = `r pretty_fixed_effects[2,6]`; (*&gamma;*~30~&nbsp;=&nbsp;`r pretty_fixed_effects[4,3]`, SE =&nbsp;`r pretty_fixed_effects[4,4]`. *t* = `r pretty_fixed_effects[4,5]`, *p* = `r pretty_fixed_effects[4,6]`)).
There was no effect of lexical stress (*&gamma;*~02~&nbsp;=&nbsp;`r pretty_fixed_effects[9,3]`, SE =&nbsp;`r pretty_fixed_effects[9,4]`. *t* = `r pretty_fixed_effects[9,5]`, *p* = `r pretty_fixed_effects[9,6]`)), but there was a main effect of group on the intercept which corroborates the plots in that L2 speakers predicted less than SS (AE: *&gamma;*~01~&nbsp;=&nbsp;`r pretty_fixed_effects[5,3]`, SE =&nbsp;`r pretty_fixed_effects[5,4]`. *t* = `r pretty_fixed_effects[5,5]`, *p* = `r pretty_fixed_effects[5,6]`; AM: *&gamma;*~11~&nbsp;=&nbsp;`r pretty_fixed_effects[6,3]`, SE =&nbsp;`r pretty_fixed_effects[6,4]`. *t* = `r pretty_fixed_effects[6,5]`, *p* = `r pretty_fixed_effects[6,6]`; AE: *&gamma;*~21~&nbsp;=&nbsp;`r pretty_fixed_effects[7,3]`, SE =&nbsp;`r pretty_fixed_effects[7,4]`. *t* = `r pretty_fixed_effects[7,5]`, *p* = `r pretty_fixed_effects[7,6]`; AM: *&gamma;*~31~&nbsp;=&nbsp;`r pretty_fixed_effects[8,3]`, SE =&nbsp;`r pretty_fixed_effects[8,4]`. *t* = `r pretty_fixed_effects[8,5]`, *p* = `r pretty_fixed_effects[8,6]`). 
The estimates for the intercept also demonstrate that IM were the ones that anticipated less in comparison with the SS.
There was also an effect caused by the group AE in the linear term (*&gamma;*~12~&nbsp;=&nbsp;`r pretty_fixed_effects[10,3]`, SE =&nbsp;`r pretty_fixed_effects[10,4]`. *t* = `r pretty_fixed_effects[10,5]`, *p* = `r pretty_fixed_effects[10,6]`), which reveals that the slope for this group is steeper than for SS.
This steeper slope means that AE tended to increased its fixations on the target more abruptly than SS. 
That is, AE anticipated more abruptly.
The lack of an interaction between the linear term and the other L2 groups reveal that they followed a more similar pattern of prediction to SS in terms of steepness.
There was an effect of all groups in the quadratic term with higher estimates for L2 groups (AE: *&gamma;*~13~&nbsp;=&nbsp;`r pretty_fixed_effects[14,3]`, SE =&nbsp;`r pretty_fixed_effects[14,4]`. *t* = `r pretty_fixed_effects[14,5]`, *p* = `r pretty_fixed_effects[14,6]`; AM: *&gamma;*~23~&nbsp;=&nbsp;`r pretty_fixed_effects[15,3]`, SE =&nbsp;`r pretty_fixed_effects[15,4]`. *t* = `r pretty_fixed_effects[15,5]`, *p* = `r pretty_fixed_effects[15,6]`; AE: *&gamma;*~33~&nbsp;=&nbsp;`r pretty_fixed_effects[16,3]`, SE =&nbsp;`r pretty_fixed_effects[16,4]`. *t* = `r pretty_fixed_effects[16,5]`, *p* = `r pretty_fixed_effects[16,6]`; AM: *&gamma;*~04~&nbsp;=&nbsp;`r pretty_fixed_effects[17,3]`, SE =&nbsp;`r pretty_fixed_effects[17,4]`. *t* = `r pretty_fixed_effects[17,5]`, *p* = `r pretty_fixed_effects[17,6]`) that indicates that the quadratic curve was more bowed for the L2 speakers, reflecting their delay with respect to SS in predicting.
Lastly, there was an interaction effect in the quadratic term between AE and lexical stress (*&gamma;*~36~&nbsp;=&nbsp;`r pretty_fixed_effects[30,3]`, SE =&nbsp;`r pretty_fixed_effects[30,4]`. *t* = `r pretty_fixed_effects[30,5]`, *p* = `r pretty_fixed_effects[30,6]`) and between AM and lexical stress (GroupAM x Lexical stress: *&gamma;*~00~&nbsp;=&nbsp;`r pretty_fixed_effects[31,3]`, SE =&nbsp;`r pretty_fixed_effects[31,4]`. *t* = `r pretty_fixed_effects[31,5]`, *p* = `r pretty_fixed_effects[31,6]`). 
This interaction confirms the information advanced by plots in Figures 3 and 4 in that advanced L2 learners fixated more on the target in the preterit tense than they did in the present tense.
This increased number of fixations reveals that preterit tense may be easier to anticipate than present tense.

Pairwise comparisons extend the results on performance differences across L2 groups. 
The pairwise comparisons are in Appendices 4, 5, 6 and 7.
In terms of L1, there is only a slightly difference in the quadratic term for the L1 English speakers (*&gamma;*~19~&nbsp;=&nbsp;`r pretty_pairwise_table_en[6,3]`, SE =&nbsp;`r pretty_pairwise_table_en[6,4]`. *t* = `r pretty_pairwise_table_en[6,5]`, *p* = `r pretty_pairwise_table_en[6,6]`), such that IE anticipate less than AE in the preterit tense.
This finding contrasts with their performance in the present tense, where IE anticipate more than AE, although the prediction difference there between the two groups does not reach significance.
As for L1 Mandarin Chinese speakers, AM and IM only differ in the intercept, where IM is shown to predict less than AM averaging across time course and stress conditions (*&gamma;*~08~&nbsp;=&nbsp;`r pretty_pairwise_table_ma[1,3]`, SE =&nbsp;`r pretty_pairwise_table_ma[1,4]`. *t* = `r pretty_pairwise_table_ma[1,5]`, *p* = `r pretty_pairwise_table_ma[1,6]`). 
That is, AM predict better overall than IM.
Regarding L2 proficiency, IE and IM only differ in the intercept too, which reveals that IE anticipate more than IM averaging across time course and stress conditions (*&gamma;*~08~&nbsp;=&nbsp;`r pretty_pairwise_table_int[1,3]`, SE =&nbsp;`r pretty_pairwise_table_int[1,4]`. *t* = `r pretty_pairwise_table_int[1,5]`, *p* = `r pretty_pairwise_table_int[1,6]`). 
At advanced proficiencies, AM and AE only differ in the linear term (`r pretty_pairwise_table_adv[2,3]`, SE =&nbsp;`r pretty_pairwise_table_adv[2,4]`. *t* = `r pretty_pairwise_table_adv[2,5]`, *p* = `r pretty_pairwise_table_adv[2,6]`).
This estimate suggests that the increase of fixations on the target in the AM group is less steep than in the AE group.
In other words, AM predict more smoothly than AE in both stress conditions.

The model estimated probability of fixations on the target above 50% chance in lexical stress conditions across all groups at the offset of the first syllable in the verb (SS x present: probability = `r printnum(model_preds$target_offset_preds[1,6])`, LB = `r printnum(model_preds$target_offset_preds[1,7])`, UB = 
`r printnum(model_preds$target_offset_preds[1,8])`; SS x preterit: probability = `r printnum(model_preds$target_offset_preds[2,6])`, LB = `r printnum(model_preds$target_offset_preds[2,7])`, UB = 
`r printnum(model_preds$target_offset_preds[2,8])`; AE x present: probability = `r printnum(model_preds$target_offset_preds[3,6])`, LB = `r printnum(model_preds$target_offset_preds[3,7])`, UB = `r printnum(model_preds$target_offset_preds[3,8])`; AE x preterit: probability = `r printnum(model_preds$target_offset_preds[4,6])`, LB = `r printnum(model_preds$target_offset_preds[4,7])`, UB = `r printnum(model_preds$target_offset_preds[4,8])`; AM x present: probability = `r printnum(model_preds$target_offset_preds[5,6])`, LB = `r printnum(model_preds$target_offset_preds[5,7])`, UB = `r printnum(model_preds$target_offset_preds[5,8])`; AM x preterit: probability = `r printnum(model_preds$target_offset_preds[6,6])`, LB = `r printnum(model_preds$target_offset_preds[6,7])`, UB = `r printnum(model_preds$target_offset_preds[6,8])`; IE x present: probability = `r printnum(model_preds$target_offset_preds[7,6])`, LB = `r printnum(model_preds$target_offset_preds[7,7])`, UB = 
`r printnum(model_preds$target_offset_preds[7,8])`; IE x preterit: probability = `r printnum(model_preds$target_offset_preds[8,6])`, LB = `r printnum(model_preds$target_offset_preds[8,7])`, UB = 
`r printnum(model_preds$target_offset_preds[8,8])`; IM x present: probability = `r printnum(model_preds$target_offset_preds[9,6])`, LB = `r printnum(model_preds$target_offset_preds[9,7])`, UB = 
`r printnum(model_preds$target_offset_preds[9,8])`; IM x preterit: probability = `r printnum(model_preds$target_offset_preds[10,6])`, LB = `r printnum(model_preds$target_offset_preds[10,7])`, UB = 
`r printnum(model_preds$target_offset_preds[10,8])`).
These probabilities are contained in Table 1.
These probabilities indicate that all groups are likely to anticipate above chance except for IM.
They also indicate that prediction probability in SS speakers is higher than in the L2 groups.
The probabilities also reflect the striking performance of AE, in the sense that their anticipation probability in present tense decreases from intermediate proficiency levels.
In contrast, the probabilities for the Mandarin speakers suggest that they improve more in anticipation performance in this tense over proficiency.

The data in this study revealed that Mandarin speakers generally improved over proficiency, as evidenced by increased gaze fixations on the target verb upon hearing the lexically stressed initial syllable. 
English speakers improved in the preterit tense condition but not in the present tense condition, where they in fact got worse. IE anticipated better than IM, but at advanced levels AM catch up with AE
SS anticipated better than the L2 speakers.
Stress condition yielded overall no significant differences.