---
title             : "The title"
shorttitle        : "Title"

author: 
  - name          : ""
    affiliation   : ""
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "my@email.com"
  - name          : ""
    affiliation   : ""

affiliation:
  - id            : ""
    institution   : ""

bibliography      : 
  - "../references.bib" 
          
floatsintext      : yes
figurelist        : yes
tablelist         : yes
footnotelist      : yes
linenumbers       : yes
mask              : yes
draft             : yes

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_word
---

```{r setup, include = FALSE, warning = FALSE}
library("papaja")
library("officer")
library("flextable")
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

```{r, 'source-scripts-models', include = FALSE}
#source(here::here("scripts", "02_load_data.R"))
source(here::here("scripts", "01_helpers.R"))

# Get path to saved models
gca_ss_mods_path  <- here("mods", "stress", "gca")
gca_en_mods_path  <- here("mods", "use_prof", "gca")

# Load models as list and store full mod to global env
load(paste0(gca_ss_mods_path, "/gca_mon_mods_sum.Rdata"))
load(paste0(gca_en_mods_path, "/gca_en_mods.Rdata"))
load(paste0(gca_ss_mods_path, "/model_preds_sum.Rdata"))
load(paste0(gca_en_mods_path, "/model_preds_en.Rdata"))

```




```{r, 'plot-time-course', echo=FALSE, fig.cap="Figure 3. Gaze fixation patterns on target from 500 ms before target syllable offset to 1000 ms after as a function of L1 and stress condition."}
knitr::include_graphics(
  here("figs", "use_prof", "gca", "timecourse_tense.png")
)
```


```{r, 'write-up-prep-mon', warning=F, eval=T}
# Prepare table to support easy in-line printing of equations

params <- gca_mod_mon_final %>% #gca_mon_mods_sum$
  tidy_lme4() %>% 
  rename(B = Estimate)

params$subscript <- 
  c(paste0(0:3, 0)) 

params <- tibble::column_to_rownames(params, 'subscript')

params$subscript <- 
  c(paste0(0:3, 0)) 

# Shortcut for inline reporting from the above table
report_row <- function(row_name) report_fixef_row(params, row_name)

# # Pre-calculate intercept as proportion
# b0 <- params$B[params$subscript == "00"] %>% as.numeric
# b0_prop <- b0 %>% inv_logit %>% round(2) %>% remove_leading_zero

```


```{r, table-mon-params, warning=F}

# Get full mod and make it pretty for the table
pretty_fixed_effects <- gca_mon_mods$gca_mod_mon_final %>%  
  tidy_lme4() %>% 
  mutate(p = format_pval(p), 
         Parameter = fix_param_names(Parameter)) %>% 
  mutate_each(funs(format_fixef_num), Estimate:t) %>% 
  rename(`_t_` = t, `_p_` = p) 

# Include gammas (Gij) after each parameter name
subs <- c(paste0(0:2, 0))
var_labels <- parenthesize(paste0(emphasize("&gamma;"), "~", subs, "~"))
pretty_fixed_effects$Parameter %<>% paste(., var_labels)

pretty_fixed_effects %>% 
  select(-effect) %>%
  knitr::kable(format = "pandoc", align = str_tokenize("lrrrr")) 


```

We conducted a GCA on SS and took them as reference when discussing our findings.
Figure 4 shows the GCA model fit for SS.
The GCA intercept for SS was positive and significant, indicating this group was anticipating at suffix onset.
The probability of SS fixating on the target was 0.953 (LB = 0.942; UB = 0.962) averaging across stress conditions, which indicates they were fixating on the target verb above chance at suffix onset.
There were main effects on the linear (`r report_row('2')`) and quadratic (`r report_row('3')`) polynomial time terms.
Since they improved the model, we kept them.


```{r, table-mon-probs, eval=T, echo=F, include = F}

border_1 <- fp_border(width = 1.5)
border_2 <- fp_border(width = 0.75)


target_offset_preds_mon %>% #model_preds$
  mutate(stress = if_else(stress == 1, "Present", "Preterit")) %>% 
  arrange(stress) %>% 
  group_by(stress) %>%
  distinct() %>%
  #ungroup() %>%
  mutate(
         stress = blank_same_as_last(as.character(stress))) %>%
  select(`Lexical stress` = stress, Probability = prob,
         LB = prob_lb, UB = prob_ub) %>%
  flextable() %>% 
  width(., j = c(2, 3, 4), width = c(1.1, 1.3, 1.1)) %>%
  font(., fontname = "Times", part = "all") %>%
  fontsize(., size = 11) %>% 
  border_remove(.) %>%  
  border(., part = "header", 
            border.top = border_1,
            border.bottom = border_2) %>% 
  hline_bottom(., part = "body", border = border_1)

```


```{r, 'plot-preds-mon', echo=FALSE, fig.cap="Figure 4. Growth curve analysis estimates of fixations on target as a function of lexical stress for the Spanish monolingual speakers during the analysis window. Lines represent model estimates, and the transparent ribbons represent ±SE. Empirical logit values on y-axis correspond to proportions of 0.12, 0.50, 0.88, and 0.98. The horizontal dotted line represents the 50% probability of fixating on the targets. The vertical dotted line indicates 200 ms after the offset of the target syllable."}
knitr::include_graphics(
  here("figs", "stress", "gca", "stress_mon.png")
)
```




```{r, 'write-up-prep-dele', warning=F, eval=T}
# Prepare table to support easy in-line printing of equations
# params <- pretty_fixed_effects %>% 
#  rename(B = Estimate)

params <- gca_en_mods$gca_en_mod_final %>%
  tidy_lme4() %>% 
  rename(B = Estimate)

params$subscript <- 
  c(paste0(0:3, 0), paste0(0:3, 1),
    paste0(0:3, 2), paste0(0:1, 3))

params <- tibble::column_to_rownames(params, 'subscript')

params$subscript <- 
  c(paste0(0:3, 0), paste0(0:3, 1),
    paste0(0:3, 2), paste0(0:1, 3))

# Shortcut for inline reporting from the above table
report_row <- function(row_name) report_fixef_row(params, row_name)

```

```{r, table-dele-params, warning=F}

# Get full mod and make it pretty for the table
pretty_fixed_effects <- gca_en_mods$gca_en_mod_final %>%
  tidy_lme4() %>% 
  mutate(p = format_pval(p), 
         Parameter = fix_param_names(Parameter)) %>% 
  mutate_each(funs(format_fixef_num), Estimate:t) %>% 
  rename(`_t_` = t, `_p_` = p) 

# Include gammas (Gij) after each parameter name
subs <- c(paste0(0:3, 0), paste0(0:3, 1), 
          paste0(0:2, 2))
var_labels <- parenthesize(paste0(emphasize("&gamma;"), "~", subs, "~"))
pretty_fixed_effects$Parameter %<>% paste(., var_labels)

pretty_fixed_effects %>% 
  select(-effect) %>%
  knitr::kable(format = "pandoc", align = str_tokenize("lrrrr")) 


```

Table 2: Growth curve model fixed effects for L2 speakers (proficiency).


```{r, table-dele-probs, eval=T, echo=F}

border_1 <- fp_border(width = 1.5)
border_2 <- fp_border(width = 0.75)


probs_l2 <- model_preds_en$target_offset_preds_en %>%
  mutate(Stress = if_else(Stress == 1, "Oxytone\n(preterit)", "Paroxytone\n(present)"),
         Stress = fct_relevel(Stress, 'Paroxytone\n(present)')) %>% 
  arrange(Stress, DELE) %>% 
  group_by(Stress, DELE) %>%
  distinct() %>%
  #ungroup() %>%
  mutate(
         Stress = blank_same_as_last(as.character(Stress)),
         DELE = blank_same_as_last(as.character(DELE))) %>%
  select(`Lexical stress` = Stress, Proficiency = DELE, `Spanish use`, Probability = prob,
         LB = prob_lb, UB = prob_ub) %>%
  flextable() %>% 
  colformat_num(., digits = 2) %>%
  width(., j = c(2, 3, 4), width = c(1.1, 1.3, 1.1)) %>%
  font(., fontname = "Times", part = "all") %>%
  fontsize(., size = 11) %>% 
  border_remove(.) %>%  
  border(., part = "header", 
            border.top = border_1,
            border.bottom = border_2) %>% 
  hline_bottom(., part = "body", border = border_1)


save_as_docx(probs_l2, path = paste0(figs_path, '/prob_l2.docx'))
```

*Table 3*: Model estimates for probability of target fixations ±SE at 200 ms after the target syllable offset as a function of L2 proficiency. (LB = lower bound; UP = upper bound).


```{r, 'plot-preds-dele', echo=FALSE, fig.cap="Figure 5. Growth curve analysis estimates of fixations on target for L2 speakers during the analysis window. Lines represent model estimates, and the transparent ribbons represent ±SE. Empirical logit values on y-axis correspond to proportions of 0.12, 0.50, 0.88, and 0.98. The horizontal dotted line represents the 50% probability of fixating on the targets. The vertical dotted line indicates 200 ms after the offset of the first syllable in the verb."}
knitr::include_graphics(
  here("figs", "use_prof", "gca", "en_gca_all_cropped.png")
)
```

# Other plots



# Tables 

## Model estimates at target syllable offset  

```{r, table-target-offset-props, eval=T, echo=F}

border_1 <- fp_border(width = 1.5)
border_2 <- fp_border(width = 0.75)

mon_preds %>% 
  mutate(cond = if_else(stress == 1, "Present", "Preterit")) %>% 
  # arrange(cond, ospan) %>% 
  arrange(cond) %>%
  group_by(cond) %>%
  mutate(prob = mean(prob),
         prob_lb = mean(prob_lb),
         prob_ub = mean(prob_ub)) %>%
  mutate(cond = blank_same_as_last(as.character(cond))) %>%
  # group_by(cond) %>%
  # filter(., ospan == max(ospan) |
  #          ospan == min(ospan)) %>%
  # ungroup() %>%
  select(`Lexical stress` = cond, Probability = prob, #ospan, 
         LB = prob_lb, UB = prob_ub) %>%
  distinct() %>%
  flextable() %>% 
  #width(., j = c(2, 3, 4), width = c(1.1, 1.3, 1.1)) %>% 
  font(., fontname = "Times", part = "all") %>%
  fontsize(., size = 11) %>% 
  border_remove(.) %>%  
  border(., part = "header", 
            border.top = border_1,
            border.bottom = border_2) %>% 
  hline_bottom(., part = "body", border = border_1)
```
*Table 1*: Model estimates for probability of target fixations in monolinguals ±SE at 200 ms 
after the target syllable offset. (LB = lower bound; UP = upper bound).

## Fixed effects

```{r, warning=F}

# Get full mod and make it pretty for the table
pretty_fixed_effects <- gca_mon_mods$gca_mod_mon_base %>% 
  tidy_lme4() %>% 
  mutate(p = format_pval(p), 
         Parameter = fix_param_names(Parameter)) %>% 
  mutate_each(funs(format_fixef_num), Estimate:t) %>% 
  rename(`_t_` = t, `_p_` = p) 

# Include gammas (Gij) after each parameter name
subs <- c(paste0(0:3, 0))
var_labels <- parenthesize(paste0(emphasize("&gamma;"), "~", subs, "~"))
pretty_fixed_effects$Parameter %<>% paste(., var_labels)

# pretty_fixed_effects <- pretty_fixed_effects[0:4,]

pretty_fixed_effects %>% 
  select(-effect) %>%
  knitr::kable(format = "pandoc", align = str_tokenize("lrrrr")) 

```

Appendix 2. Growth Curve Analysis fixed effects (monolinguals)








```{r, warning=F}

# # Get full mod and make it pretty for the table
# pretty_fixed_effects <- gca_l2_mod_wm_final %>%  #gca_l2_mods$
#   tidy_lme4() %>% 
#   mutate(p = format_pval(p), 
#          Parameter = fix_param_names(Parameter)) %>% 
#   mutate_each(funs(format_fixef_num), Estimate:t) %>% 
#   rename(`_t_` = t, `_p_` = p) 
# 
# # Include gammas (Gij) after each parameter name
# subs <- c(paste0(0:3, 0), paste0(0:3, 1), 
#           paste0(0:3, 2))
# var_labels <- parenthesize(paste0(emphasize("&gamma;"), "~", subs, "~"))
# pretty_fixed_effects$Parameter %<>% paste(., var_labels)
# 
# pretty_fixed_effects %>% 
#   knitr::kable(format = "pandoc", align = str_tokenize("lrrrr")) 

```

Appendix 0: Growth curve model fixed effects L2 (WM)


## Random effects

```{r, 'ranef-table-mon', results = "asis"}
ranef_table <- gca_mon_mods$gca_mod_mon_final %>% 
  tidy_ranef_summary %>% 
  # Format the numbers
  mutate_each(funs(format_fixef_num), vcov, sdcor) %>%
  mutate_each(funs(format_cor), -var1, -grp, -vcov, -sdcor) %>%
  sort_ranef_grps %>%
  # Format variable names and group names
  mutate(var1 = fix_param_names(var1) %>% blank_nas,
         grp =  blank_same_as_last(grp) %>% fix_param_names) %>% 
  rename(Group = grp, Parameter = var1, Variance = vcov, SD = sdcor)

# Correlation columns need names with characters so that pandoc can align them
names(ranef_table)[5:9] <- 
  c("Correlations", "&nbsp;", " &nbsp;", "  &nbsp;", "  &nbsp;")

ranef_table %>% 
  knitr::kable(format = "pandoc", align = str_tokenize("llrrrrrr"))
```




Appendix 5.Growth curve model random effects (monolinguals)





```{r, 'ranef-table-l2', results = "asis"}
ranef_table <- gca_en_mods$gca_en_mod_final %>% 
  tidy_ranef_summary %>% 
  # Format the numbers
  mutate_each(funs(format_fixef_num), vcov, sdcor) %>%
  mutate_each(funs(format_cor), -var1, -grp, -vcov, -sdcor) %>%
  sort_ranef_grps %>%
  # Format variable names and group names
  mutate(var1 = fix_param_names(var1) %>% blank_nas,
         grp =  blank_same_as_last(grp) %>% fix_param_names) %>% 
  rename(Group = grp, Parameter = var1, Variance = vcov, SD = sdcor)

# # Correlation columns need names with characters so that pandoc can align them
# names(ranef_table)[5:9] <- 
#   c("Correlations", "&nbsp;", " &nbsp;", "  &nbsp;", "  &nbsp;")

ranef_table %>% 
  knitr::kable(format = "pandoc", align = str_tokenize("llrrrrrr"))


```

Appendix 6: Growth curve model random effects (L2)

# References

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id = "refere"></div>
\endgroup
